Simulation of Nano Particles in a Laser Trap

### 2017-02-14 doc/draft2.tex
updates

@@

        \includegraphics[scale=0.4]{images/baro_temp_start.pdf}

@@

plotted for each of the pressure values and both temperatures.

@@

@@

@@

\newpage
\section{Conclusion}
% what does this all tell us? do we need to study more of this?

>>>>

As can be seen in Fig.~\ref{fig:lj}, the potential is very close to 0 at about $r/\sigma=2.5$. This means that any contribution of the potential
energy after this point is vanishingly small. To save computing time it is common practice to cut off the potential at a certain point and don't
calculate the contribution for distances beyond that. The cut-off distance for this thesis was set to $r = 2.5\sigma$.\\

@@

        \includegraphics[scale=0.4]{images/baro_temp_long_new.pdf}

@@

plotted for each of the pressure values and both temperatures, which can be seen in~\ref{fig:comintout}.

@@

        \caption{The temperature of the center of mass, the internal temperature and the outgoing temperature of the surrounding gas as functions of
            heat being pumped into the system, for pressures
        $P=0.1$, $P=0.5$ and $P=1$ at impinging gas temperatures of $T_\text{imp}=0.05$ (red) and $T_\text{imp}=0.1$. The three columns each show 
        a fixed pressure value and the rows show fixed measured quantities. As the pressure relates to the maximum amount of heat that can be injected
    into the system, the ranges on the abscissa in one row is different for every plot.}
        \label{fig:comintout}

@@

The three columns of the plot correspond to fixed pressure values and different measured quantities, whereas every row corresponds to a fixed measured
quantity at different pressures. As previously mentioned, the amount of pressure relates to the number of surrounding particles and thus limits the
amount of heat that can be pumped into the system. Therefore, the range of values in the abscissa differs for different pressures -- at $P=0.1$ the
values of $\Delta Q$ range from $0$ to $0.02$ and at $P=1.0$ from $0$ to $0.5$.\\
The first thing that is noticable, is the increase of the temperature of the center of mass, the internal temperature and the outgoing gas temperature
with increasing $\Delta Q$. This makes sense, as the amount of heat that is put into the system is also transfered in the interaction between the nano
particle and the surrounding gas.\\
One observation that is not so obvious due to the different ranges of $\Delta Q$ values: all temperature values increase faster for low pressures and
increase slower for higher pressures. Take the center of mass temperature for $P=0.1$ and $P=1$ at $T=0.05$ (red line) as an example: while it reaches
a value of a $T_\text{com} = 0.1$ at about $\Delta Q = 0.015$ at $P=0.1$, it takes a $\Delta Q$ of a little under $0.1$ to achieve the same value.
This can be observed for every one of the three quantities. This is to be expected, as the surrounding gas acts as a thermostat. \\
The development of the different temperatures seem to be depending of the temperature of the surrounding gas as well. The blue curves (which
correspont do a surrounding gas temperature of $T=0.1$) are growing slightly faster than the red curves ($T=0.05$).\\
In their paper~\cite{MillenJ.2014} Millen et al. give a formula for the center of mass temperature:
    T_\text{COM} = \frac{T_\text{imp}^{3/2}+\tfrac\pi 8 \ T_\text{em}^{3/2}}{T_\text{imp}^{1/2}+\tfrac\pi8 T_\text{em}^{1/2}}
This formula together with the measured values of $T_\text{imp}$ and $T_\text{em}$ can be used to compare the results. The comparison between the
calculated and the measured value can be seen for a representative choice of parameters in Fig.~\ref{fig:measurevscalc}.

@@

\newpage
\section{Conclusion and Further Remarks}
% what does this all tell us? do we need to study more of this? 
In this thesis I have modeled an optical tweezer experiment with methods from the field of computational physics. The experiment was broken down into
different sections, that have been modeled separately. With the use of molecular dynamics I simulated the behaviour of a nano particle in a laser trap
and investigated the effects of the laser power and temperature of the surrounding gas on the center of mass movement of the nano particle.\\
The results show, that the center of mass temperature (and thus its movement) does indeed depend on the energy of the laser, as well as on the
pressure and temperature of the surrounding gas.\\
The development of the center of mass temperature shows a curve that seems to have a convex form, whereas the internal temperature shows a more
concave behaviour. So while the internal temperature initially grows faster, it could be possible for the center of mass temperature to pass the
internal temperature.\\
There are several ways to explore this subject further. The first idea would be to decrease the pressure even more and investiate the case of very low
energies, since this is not easily feasible in an experimental setup. Another idea would be to increase the number of atoms in the nano particle to
see if the surface of the particle plays a role in the development of the temperatures. Furthermore, the interaction between the gas particles and the
nano particle in the trap could be varied to include an attractive part in the potential. Generally, these simulations could be expanded by running
them on faster computers to investigate long term behaviour of the systems and expand the ranges of the different values like pressure or laser
energy.
